Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-01-12 manuscript/manuscript.Rmd
updated figure 1

```{r figure_1, dependson="plot-options", fig.cap="Boxplots of model residuals for one-step-ahead forecasts at each observation year. Each one-step forecast was simulated `r nSims` times. Note that the y-axes vary across panels.", fig.width=8, fig.height=8, cache=FALSE, results='hide'}

@@

  ggtitle(expression(italic("P. secunda")))+

@@

pFinal

>>>>

```{r figure_1, dependson="plot-options", fig.cap="Boxplots of model residuals for one-step-ahead forecasts at each observation year for each quadrat. Residuals represent the difference in observed and predicted cover change from year $t-1$ to year $t$. Each one-step forecast was simulated 100 times for each quadrat. Note that the y-axes vary across panels.", fig.width=8, fig.height=8, cache=FALSE, results='hide'}

@@

  ggtitle(expression(italic("Poa secunda")))+

@@

# pFinal

### 2015-01-12 manuscript/manuscript.tex
updated figure 1

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_1.pdf}
\caption{Boxplots of model residuals for one-step-ahead forecasts at
each observation year. Each one-step forecast was simulated
\texttt{r nSims} times. Note that the y-axes vary across panels.}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_1.pdf}
\caption{Boxplots of model residuals for one-step-ahead forecasts at
each observation year for each quadrat. Residuals represent the
difference in observed and predicted cover change from year $t-1$ to
year $t$. Each one-step forecast was simulated 100 times for each
quadrat. Note that the y-axes vary across panels.}
\end{figure}
